Strings functions analysis

### 2022-08-28 article.tex
all java functions added

    Below in section \ref{tab:my_label} is a table with the results - metrics. It is important to note that these results take into account the methods of languages from their standard libraries.

@@

    An interesting fact was that, judging by the popularity of the use, the immutable methods are superior to the mutable ones.

@@

>>>>

    Below in section \ref{tab:my_label} is a table with the results - metrics. It is important to note that these results take into account the functions of languages from their standard libraries.

@@

    An interesting fact was that, judging by the popularity of the use, the immutable functions are superior to the mutable ones.

@@

    \subsection{String function metrics}

    \subsection{String functions of standard libraries}

    \textbf{Java}: charAt, codePointAt, codePointBefore, codePointCount, compareTo, compareToIgnoreCase, concat, contains, contentEquals, copyValueOf, endsWith, equals, equalsIgnoreCase, format, getBytes, getChars, hashCode, indexOf, intern, isEmpty, length, lastIndexOf, length, matches, offsetByCodePoints, regionMatches, replace, replaceAll, replaceFirst, split, startsWith, subSequence, substring, toCharArray, toLowerCase, toString, toUpperCase, trim, valueOf.
